Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2024-12-29 paper/paper.tex
Update paper

1. In order to start interpreter sessions, Litrepl allocates resources as shown
on the Figure \ref{fig:resource-allocation}. First, the auxilary directory is
created using the name, computed from the current interpreter class, working
directory and the name of a system folder for temporary files.  Next, the two
POSIX pipes, in.pipe and out.pipe, are created. Finally, the configured
interpreter is started with the pipes attached.

>>>>

To initiate interpreter sessions, Litrepl allocates resources as depicted in
Figure \ref{fig:resource-allocation}. The process begins by creating an
auxiliary directory. The name of this directory is derived from the combination
of the current interpreter class name, the Litrepl working directory, and a
system-designated folder for temporary files. Subsequently, two POSIX
pipes—\texttt{in.pipe} and \texttt{out.pipe} are established. The configured
interpreter is then launched with these pipes attached, and the interpreter's
process identifier is recorded in a dedicated file.

The initialization routine incorporates additional open calls on the pipes to
prevent premature termination of the interpreter due to detachments. This
ensures the interpreter remains active and responsive.

When an evaluation request is received, Litrepl calculates the name of the
anticipated response storage file and forwards the request to the interpreter.
It concurrently initiates a response reader process. The response storage is
secured using soft POSIX file locks, enabling the main process to ascertain when
the response is ready. In instances where the response exceeds the configured
time to completion, Litrepl provides a partial result. This partial result can
be updated with complete details in subsequent calls. The format for a partial
result section appears as follows:
% Displaying a verbatim box above two columns in a two-column paper

\begin{comment}
\begin{sh}
echo -n '\begin' ; echo '{verbatim}'
echo '\begin{result}'
litrepl --python-auxdir=/tmp/litrepl/python restart python
{
cat <<EOF
import time
print('... some output ...')
time.sleep(9999)
EOF
}|litrepl --python-auxdir=/tmp/litrepl/python --timeout=1,inf eval-code python
echo '\end{result}'
echo -n '\end'; echo '{verbatim}'
\end{sh}
\end{comment}

\begin{figure*}[t]
  \centering
  \begin{minipage}{\textwidth}
    \centering
    %lresult
    \begin{verbatim}
    \begin{result}
    ... some output ...
    [LR:/tmp/litrepl/python/partial_7b81e1e.txt]
    \end{result}
    \end{verbatim}
    %lnoresult
  \end{minipage}
  \caption{Example output in a verbatim format displayed above two columns.}
  \label{fig:verbatim_example}
\end{figure*}

% The figure* environment is used to span two columns, while a minipage is
% used to contain the verbatim listing. This code creates a box above the
% two-column layout with a caption explaining the contents.
